### 2018-11-22 Chapters/KaneMele.tex
minor

This describes a type of anisotropic exchange interaction known as XXZ Heisenberg model for next nearest neighbors. If the laser field is not too strong $\tilde{J}_{ij}(t) > 0$, and, in the $\hat{e}_z$ direction this interaction will compete against the exchange interaction $J_{ij}(t)$. The reason for this is that being $J_{ij}(t) > 0$ the spins will try to attain antiferromagnetic order, which means that next nearest neighbor spin will tend to be aligned. The effect of $\tilde{J}_{ij}(t)$ will be the opposite, forcing the next nearest neighbor spins to be in opposite directions. In general the strength of the exchange interaction will be larger and the net effect of $\tilde{J}_{ij}(t)$ will be a tilting of the spins towards the $\hat{e}_x$-$\hat{e}_y$ plane.

>>>>

This describes a type of anisotropic exchange interaction known as XXZ Heisenberg model for next nearest neighbors. The same spin model is obtain in \cite{Rachel2010} without the laser perturbation. If the laser field is not too strong $\tilde{J}_{ij}(t) > 0$, and, in the $\hat{e}_z$ direction this interaction will compete against the exchange interaction $J_{ij}(t)$. The reason for this is that since $J_{ij}(t) > 0$ the spins will try to attain antiferromagnetic order, which means that next nearest neighbor spin will tend to be aligned. The effect of $\tilde{J}_{ij}(t)$ will be the opposite, forcing the next nearest neighbor spins to be in opposite directions. In the $\hat{e}_x-\hat{e}_y$ plane, $\tilde{J}_{ij}(t)$ will favor ferromagnetic order between next nearest neighbors, which adds to the effect of $J_{ij}(t)$. In general the strength of the exchange interaction will be larger and the net effect of $\tilde{J}_{ij}(t)$ will be a tilting of the spins towards the $\hat{e}_x$-$\hat{e}_y$ plane.
